The effects of varying depth in cosmic shear surveys

### 2019-10-22 paperdraft.tex
added peter's suggestions

%\documentclass[referee]{aa}
\pdfoutput=1

@@

   \date{Received XXX; accepted XXX}

  \abstract
   {We present a semi-analytic model for the shear two-point correlation function of a cosmic shear survey with non-uniform depth. Ground-based surveys are subject to depth variations that primarily arise through varying atmospheric conditions. For a survey like the Kilo-Degree Survey (KiDS), we find that the measured depth variation increases the amplitude of the observed shear correlation function at the level of a few percent out to degree-scales, relative to the assumed uniform-depth case. The impact on the inferred cosmological parameters is shown to be insignificant for a KiDS-like survey. For next-generation cosmic shear experiments, however, we conclude that variable depth should be accounted for. \textcolor{blue}{\href{https://docs.google.com/document/d/13j7fUE8jrK5HOVbf4p0HdQs6c14jbWtm9Yq8CtLZCK4/edit?usp=sharing}{[Link to the current google doc]}}}

   \keywords{gravitational lensing --
                weak lensing --
                cosmic shear
               }

   \maketitle

@@

\textcolor{blue}{In general, the semi-analytic model predicts a stronger effect than the mocks. This is due to the fact that the mocks are subject to a redshift-cutoff at $z=2$, meaning that they do not take the high-redshift tail of galaxies into account. This is of particular importance in the first redshift bin, where this feature is especially pronounced (compare Fig.~\ref{fig:nofz_quantiles}). When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix). In particular this means that the mocks slightly underestimate the effect of varying depth.}

@@

which is a convolution of the power spectrum and the 2-dimensional sinc function \eqref{eq:sinc}. Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail. In particular, $\langle \gamma(\theta)\gamma^*(\theta')\rangle$ does not only depend on the separation vector $\theta'-\theta$, but also on the position $\theta$. For example, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.

>>>>

% \documentclass[referee]{aa}
\pdfoutput=1

@@

   \date{Received 21 October 2019; accepted XXX}

  \abstract
   {We present a semi-analytic model for the shear two-point correlation function of a cosmic shear survey with non-uniform depth. Ground-based surveys are subject to depth variations that primarily arise through varying atmospheric conditions. For a survey like the Kilo-Degree Survey (KiDS), we find that the measured depth variation increases the amplitude of the observed shear correlation function at the level of a few percent out to degree-scales, relative to the assumed uniform-depth case. The impact on the inferred cosmological parameters is shown to be insignificant for a KiDS-like survey. For next-generation cosmic shear experiments, however, we conclude that variable depth should be accounted for.}

   % \keywords{gravitational lensing --
   %              weak lensing --
   %              cosmic shear
   %             }
   \keywords{gravitational lensing: weak -- cosmology: miscellaneous}
   \maketitle

@@

In general, the semi-analytic model predicts a stronger effect than the mocks. This is due to the fact that the mocks are subject to a redshift-cutoff at $z=2$, meaning that they do not take the high-redshift tail of galaxies into account. This is of particular importance in the first redshift bin, where this feature is especially pronounced (compare Fig.~\ref{fig:nofz_quantiles}). When the same cutoff is applied to the models, the agreement on sub-pointing scales is striking (compare Fig.~\ref{fig:redshift_cutoff} in the Appendix). In particular this means that the mocks slightly underestimate the effect of varying depth.

@@

which is a convolution of the power spectrum and the 2-dimensional sinc function \eqref{eq:sinc}. Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail. In particular, $\langle \gamma(\b \theta)\gamma^*(\b \theta')\rangle$ does not only depend on the separation vector $\b \theta'-\b \theta$, but also on the position $\b \theta$. For example, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.
